FINE SCALE REGISTRATION OF SIDEWALKS AND OTHER RIBBON-LIKE FEATURES FROM AERIAL IMAGERY

### 2018-08-20 Chapters/1.Introduction/Introduction.tex
Updates from ShareLaTeX

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{Figures/Goal.png}
    \caption[Objective Demonstration]{A demonstration  on input data and output result. By given the input map and initial trajectory (left), we produce the precious boundaries(right) with our \ac{DP} approach. The trajectory mark in black and the boundaries mark in red. We output the edges information as a .geojson file which allow us to edit and change with the given input file.}
    \label{fig:goal}
\end{figure}

@@

In addition, poorly registered walking paths could confound any algorithm that might hope to automatically locate features on the path including obstacles, damage, overgrowth, or stairways that could impact the walk-ability. 
Several authors\cite{femiani2009interval, femiani2007road} have worked on segmenting streets and sidewalks or other linear features directly from aerial imagery; however sidewalks are much thinner than streets and are often partially occluded. 
More importantly, these methods are mainly concerned with the connectivity of the extracted pathways and not with identifying the precise boundaries. 
Figure \ref{fig:goal} shows the input map with the initial trajectory (left) and result from our approach (right), we marked initial trajectory in black and boundaries in red.
Figure \ref{fig:fw_ov} demonstrate the step by step detail diagram for our approach, from the input map (a), along with the initial trajectory(b), we can generate the ribbon-image with the given mid-curve(c). 
We generate the initial estimation for each pixels(d) with initial density along the ribbon-image, then apply our approach with \ac{DP} solution(e). 
Our approach can be used to refine or recover the thickness of street networks or other networks of ribbon-like features. Several automatic approaches model segmentation as a \ac{CRF} in order to ensure that the resulting output configurations are plausible \cite{ActiveContou09, Rother2004-ou, Achanta:149300}.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{Figures/Challenge.png}
    \caption[Challenges Demonstration]{A detail demonstrations on challenges that we are facing in our approach. From left to right, top to bottom, it shows that sidewalk are under the shadow, camouflage with adjacent materials and blocked by obstacles.}
    \label{fig:challenge_demo}
\end{figure}

@@

The aim of this work is to precisely align and determine the width of a coarsely registered ribbon-like feature to match its appearance in a \ac{VHR} image.
The input is a \ac{VHR} georeferenced and orthorectified image along with a set of linear features that are close to, but perhaps not precisely aligned with the center of a ribbon-like feature. 
In particular, we expect that the ribbon will be made of a material with a somewhat uniform appearance (e.g. asphalt, gravel, or concrete) but that its appearance will be affected by shadows and interrupted by occlusions from vegetation, pedestrians, or vehicles such as bicycles. 
Our aim is to determine a more precise mid-line and an estimate for the width of the ribbon-like feature, which can very slowly along its trajectory. 
The solution proposed in this paper does not rely on prior knowledge of the material on or around the ribbon, but instead, it estimates material appearance as it refines the placement of an initial estimate for the ribbon's mid-line.

	Our contributions are as follows:
	\begin{itemize}
		\item A novel \ac{DP} approach is proposed for aligning ribbon-like features to orthoimaagery.
		\item We do not require large training sets; a few parameters to control the smoothness of the resulting ribbon along with a coarse initial estimate of the trajectory are all that is needed.
		\item Unlike methods that aim to recover the trajectories only, in our approach a likely thickness is directly identified so that more plausible trajectories and boundaries can be identified.
		\item An application to the problem of registering sidewalks to aerial photographs is demonstrated, allowing \ac{GIS} data sets to be improved as high-resolution ortho imagery becomes available. 
	\end{itemize}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{Figures/Goal.png}
    \caption[Objective Demonstration]{A demonstration  on input data and output result. With the input map and initial trajectory (left), we produce the precious boundaries(right) with our \ac{DP} approach. The trajectory mark in black and the boundaries mark in red. We output the edges information as a .geojson file which allow us to edit and change with the given input file.}
    \label{fig:goal}
\end{figure}

@@

In addition, poorly registered walking paths could confound any algorithm that might hope to automatically locate features on the path including obstacles, damage, overgrowth, or stairways that could impact the walk-ability. 
Several authors\cite{femiani2009interval, femiani2007road} have worked on segmenting streets and sidewalks or other linear features directly from aerial imagery; however sidewalks are much thinner than streets and are often partially occluded. 
More importantly, these methods are mainly concerned with the connectivity of the extracted pathways and not with identifying the precise boundaries. 
Figure \ref{fig:goal} shows the input map with the initial trajectory (left) and result from our approach (right).
We marked initial trajectory in black and boundaries in red.
Figure \ref{fig:fw_ov} demonstrates the step by step detail diagram for our approach, from the input map (a), along with the initial trajectory(b), we can generate the ribbon-image with the given mid-curve(c). 
We generate the initial estimation for each pixels(d) with initial density along the ribbon-image, then apply our approach with \ac{DP} solution(e). 
Our approach, we name it \ac{DPST}, can be used to refine or recover the thickness of street networks or other networks of ribbon-like features. Several automatic approaches model segmentation as a \ac{CRF} in order to ensure that the resulting output configurations are plausible \cite{ActiveContou09, Rother2004-ou, Achanta:149300}.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{Figures/Challenge.png}
    \caption[Challenges Demonstration]{A detail demonstrations of challenges that we are facing in our approach. From left to right, top to bottom, it shows that sidewalk are under the shadow, camouflage with adjacent materials and blocked by obstacles.}
    \label{fig:challenge_demo}
\end{figure}

@@

The aim of this work is to precisely align and determine the width of a coarsely registered ribbon-like feature to match its appearance in a \ac{VHR} image.
The input is a \ac{VHR} georeferenced and orthorectified image along with a set of linear features that are close to, but perhaps not precisely aligned with the center of a ribbon-like feature. 
In particular, we expect that the ribbon will be made of a material with a somewhat uniform appearance (e.g. asphalt, gravel, or concrete) but that its appearance will be affected by shadows and interrupted by occlusions from vegetation, pedestrians, or vehicles such as bicycles. 
Our aim is to determine a more precise mid-line and an estimate for the width of the ribbon-like feature, which can vary slowly along its trajectory. 
The solution proposed in this paper does not rely on prior knowledge of the material on or around the ribbon, but instead, it estimates material appearance as it refines the placement of an initial estimate for the ribbon's mid-line.

	Our contributions are as follows:
	\begin{itemize}
		\item A novel \ac{DP} approach is proposed for aligning ribbon-like features to orthoimagery.
		\subitem We do not require large training sets; a few parameters to control the smoothness of the resulting ribbon along with a coarse initial estimate of the trajectory are all that is needed.
		\subitem Unlike methods that aim to recover the trajectories only, in our approach a likely thickness is directly identified so that more plausible trajectories and boundaries can be identified.
		\item An application to the problem of registering sidewalks to aerial photographs is demonstrated, allowing \ac{GIS} data sets to be improved as high-resolution ortho imagery becomes available. 
	\end{itemize}

### 2018-08-20 Chapters/2.Theory/Background.tex
Updates from ShareLaTeX

\ac{VHR} stands for Very High Resolution, it has advantageous for buildings extraction, road detection or image segmentation~\cite{FREIRE20141, 10.1007/BFb0015525, 10.1007/978-3-642-15567-3_16}. 
These aerial imageries contain more information and detail due to the higher resolution, which give us the ability to develop more complex analysis on the imagery with same size.
\figref{fig:vhr_compare} demonstrates the difference between different resolution within the same area. From (a) to (c), the resolution changes from half meter scale to 10 meter scale. 
With higher resolution, it's easier to find the precious boundaries of an object or identify it. 
For building extraction, higher resolution provides more information when dealing with complex houses or extract complex suburban roofs~\cite{10.1007/BFb0015525}. 
For thin ribbon-features segmentation such as sidewalks in our approach, to visualize an overlaid map without high resolution, the imagery can be distracting, and the output may effect by tiny discrepancies between digitized pathways~\cite{10.1007/978-3-642-15567-3_16}.

@@

\section{\ac{CRF}}
\ac{CRF} stands for Conditional Random Field, which is a class of statistical modeling method that often applied in pattern recognition and machine learning~\cite{MAL-013}. 
As a type of discriminative undirected probabilistic graphical model, \ac{CRF} is commonly used for segmenting, labeling or parsing of sequential data, such as in computer vision, structure segmentation and object recognition~\cite{RuizSarmiento2015UPGMppA, 1315232, lafferty2001conditional}. 
For road segmentation, several approaches are able to locate the precise boundaries by treating it as a \ac{CRF} problem~\cite{ActiveContou09, Achanta:149300}.

@@

\ac{GMM} stands for Gaussian Mixture Models~\cite{sridharan2014gaussian}.
It is a probabilistic model for representing normally distributed subpopulations within an overall population.
\ac{GMM} often can be performed when the data points are mixtures of a Gaussian distribution. 
It can be used in common computer vision tasks such as background and foreground subtraction~\cite{1333992}. 
For road segmentation, we can treat the problem as subtract foreground (road feature) from the complex background (non-road feature). 
\figref{fig:gmm_sample_1} demonstrate the comparison between foreground and background \ac{GMM} on sample walking path show in gray-scale. 
For foreground subtraction, which shown in row 1 and row 3, we treat sidewalk texture as foreground and apply the \ac{GMM} algorithm to subtract it from the background (non-sidewalk texture). 
Background subtraction are shown in row 2 and row 4, we did the opposite and treat non-sidewalk part as foreground.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/treewithdp.png}
    \caption[Demonstration on Fibonacci Sequence]{Representing the calculation of Fibonacci Sequence ($7^{th}$) with binary tree. Row 1 shows without applying dynamic programming, it need's certain exponential rate to calculate $n^{th}$ Fibonacci number. With the increase of $n$, the number of calculation increase significantly. Row 2 shows with dynamic programming, after saving previous calculation, it's only require linear time steps to calculate $n^{th}$ Fibonacci number. We marked unnecessary steps in red X to show it's can be skipped. }
    % \cite{stack_overflow}
    \label{fig:fbs}
\end{figure}

>>>>

\ac{VHR} stands for Very High Resolution. It has advantageous for buildings extraction, road detection or image segmentation~\cite{FREIRE20141, 10.1007/BFb0015525, 10.1007/978-3-642-15567-3_16}. 
These aerial imageries contain more information and detail due to the higher resolution, which gives us the ability to develop more complex analysis on the imagery with same size.
\figref{fig:vhr_compare} demonstrates the difference between different resolution within the same area. From (a) to (c), the resolution changes from half meter scale to 10 meter scale. 
With higher resolution, it is easier to find the precious boundaries of an object or identify it. 
For building extraction, higher resolution provides more information when dealing with complex houses or extract complex suburban roofs~\cite{10.1007/BFb0015525}. 
For thin ribbon-features segmentation such as sidewalks in our approach, to visualize an overlaid map without high resolution, the imagery can be distracting, and the output may be effected by tiny discrepancies between digitized pathways~\cite{10.1007/978-3-642-15567-3_16}.

@@

\section{\ac{CRF}}
\ac{CRF} stands for Conditional Random Field, which is a class of statistical modeling methods that often applied in pattern recognition and machine learning~\cite{MAL-013}. 
As a type of discriminative undirected probabilistic graphical model, \ac{CRF} is commonly used for segmenting, labeling or parsing of sequential data, such as in computer vision, structure segmentation and object recognition~\cite{RuizSarmiento2015UPGMppA, 1315232, lafferty2001conditional}. 
For road segmentation, several approaches are able to locate the precise boundaries by treating it as a \ac{CRF} problem~\cite{ActiveContou09, Achanta:149300}.

@@

\ac{GMM} stands for Gaussian Mixture Models~\cite{sridharan2014gaussian}.
It is a probabilistic model for representing normally distributed subpopulations within an overall population.
\ac{GMM} often can be performed when the data points are mixtures of a Gaussian distribution. 
It can be used in common computer vision tasks such as background and foreground subtraction~\cite{1333992}. 
For road segmentation, we can treat the problem as subtract foreground (road feature) from the complex background (non-road feature). 
\figref{fig:gmm_sample_1} demonstrates the comparison between foreground and background \ac{GMM} on sample walking path show in gray-scale. 
For foreground subtraction, which we show in row 1 and row 3, we treat sidewalk texture as foreground and apply the \ac{GMM} algorithm to subtract it from the background (non-sidewalk texture). 
Background subtraction are shown in row 2 and row 4, we did the opposite and treat non-sidewalk part as foreground.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/treewithdp.png}
    \caption[Demonstration on Fibonacci Sequence]{Representing the calculation of Fibonacci Sequence ($7^{th}$) with binary tree. Row 1 shows without applying dynamic programming, it need's certain exponential rate to calculate $n^{th}$ Fibonacci number. With the increase of $n$, the number of calculation increase significantly. Row 2 shows with dynamic programming, after saving previous calculation, it's only require linear time steps to calculate $n^{th}$ Fibonacci number. We marked unnecessary steps in red X to show it's can be skipped. }
    \cite{stack_overflow}
    \label{fig:fbs}
\end{figure}

### 2018-08-20 Chapters/2.Theory/Theory.tex
Updates from ShareLaTeX

Another image segmentation approach that has seen extraordinary success is the use of Convolutional Neural Networks (CNNs) and transposed convolution~\cite{Badrinarayanan2017-il, Noh2015-ni, Shelhamer2017-rf, Ronneberger2015-sv}. 
Unlike the proposed approach, these have millions of tunable parameters and need significant pre-annotated data and offline training to build a model. 
In a recent exploration of learning to segment street networks from online maps~\cite{Kaiser2017-np}, built a fully convolutional network with 137 million parameters.
A similar approach with another deep architecture called U-net~\cite{Ronneberger2015-sv} was applied to the street network segmentation problem~\cite{Zhang2017-gi}.
These approaches claim to be robust to occlusion and ambiguous regions, but they benefit from a large amount of carefully annotated data that includes road width~\cite{Mnih2013-dp}. 
This type of pre-annotated data with aligned aerial imagery is much harder to obtain for walking paths. 
The proposed approach has only handful of tunable parameters with clear interpretations, so that they can be interactively set and used without offline training.

>>>>

Another image segmentation approach that has seen extraordinary success is the use of Convolutional Neural Networks (CNNs) and transposed convolution~\cite{Badrinarayanan2017-il, Noh2015-ni, Shelhamer2017-rf, Ronneberger2015-sv}. 
Unlike the proposed approach, these have millions of tunable parameters and need significant pre-annotated data and offline training to build a model. 
In a recent exploration of learning to segment street networks from online maps~\cite{Kaiser2017-np}, built a fully convolutional network with 137 million parameters.
A similar approach with another deep architecture called U-net~\cite{Ronneberger2015-sv} was applied to the street network segmentation problem~\cite{Zhang2017-gi}.
These approaches claim to be robust to occlusion and ambiguous regions, but they benefit from a large amount of carefully annotated data that includes road width~\cite{Mnih2013-dp}. 
This type of pre-annotated data with aligned aerial imagery is much harder to obtain for walking paths. 
\ac{DPST} has only handful of tunable parameters with clear interpretations, so that they can be interactively set and used without offline training.

### 2018-08-20 Chapters/3.Hypothesis/Hypothesis.tex
editing new figure and remove bad image
Updates from ShareLaTeX

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Figures/sw-figure.pdf}
    \caption[2D Ribbon Image]{A demonstration of the parameters for a ribbon in 2D. $k_n$ indicates a parameter that describes the radius of the medial curve that we considered to be part of the ribbon, $k_f$ is a distance from the medial curve that we considered very unlikely to be part of the ribbon, and $k_W$ is the maximum width of the ribbon image.}
    \label{fig:2d_ribbon}
\end{figure}

As shown in \ref{fig:2d_ribbon}, from figure \ref{fig:osm_oxford_path}, we should assume that there is some uncertainty in the position $\mathbf{x}_s$ of the medial curve and also uncertainty in the radius $r_s$ of the discredited ribbon. 
But that there is range of distances $t \in 0\dots k_n$ from the medial curve which we can accept labeling as positive examples that are within the ribbon, and that there is some range of distances $t \in k_f\dots k_W$ which we can accept labeling as negative sample. 
Finally a range $t\in (k_n+1)...(k_f-1)$ of distances that are possible locations of the ribbon's boundary.
Therefore, when searching for improved medial curves and radii of the ribbon, we can consider a discrete range of offsets $t=-k_W,..., k_W$ chosen to be wide enough that true ribbon image itself likely fits entirely within the grid of input negative samples along its edges.

The orthorectified color image $\image(x,y)$
records the color at the point $x,y$ in the image plane.
Then $\image(\mathbf{x}_{s,t}),$ is a warped version of the image in which the ribbon is centered on a single strip at $t=0$.
The situation is illustrated in \ref{fig:ribbon_3d}.  
In this warped image, we can estimate the amount $t_s$ to shift the ribbon's center in the $t-$axis, which is orthogonal to the curve,  and also the amount the radius $r_s$ so that the  ribbon at each row is in columns $(t_s - r_s)\dots(t_s+r_s)$.  
Our problem is to estimate the most likely values of $t_s$ and $r_s$.

@@

We use this assumption to estimate the probability that a pixel is part of a ribbon conditioned on its color.
Let $k_n$ be parameter that describes the radius around the medial curve that we will consider to be part of the ribbon with very high confidence. 
Let $k_f$ indicate a distance from the medial curve that we consider very unlikely to be part of the ribbon. 
Finally, let $k_W$ indicate maximum value of $t$ to consider when learning the distribution of colors in a ribbon image. 
We model the distribution of colors within the sidewalk as a Gaussian Mixture Model of $k_g=4$ full-co-variance gaussian distribution and we model the distribution of colors outside of the ribbon as a mixture $2k_g$ Gaussian since we expect more variation and complexity in this zone. 
As shown in figure \ref{fig:GMM_result}, given an initial estimate for the set of colors inside or outside of the ribbon, we estimate the weights and co-variances of the Gaussians using the \ac{EM-GMM} \cite{sridharan2014gaussian} algorithm.

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/sw-figure.pdf}
    \caption[2D Ribbon Image]{A demonstration of the parameters for a ribbon in 2D. $k_n$ indicates a parameter that describes the radius of the medial curve that we considered to be part of the ribbon, $k_f$ is a distance from the medial curve that we considered very unlikely to be part of the ribbon, and $k_W$ is the maximum width of the ribbon image.}
    \label{fig:2d_ribbon}
\end{figure}

As shown in figure \ref{fig:2d_ribbon}, from figure \ref{fig:osm_oxford_path}, we should assume that there is some uncertainty in the position $\mathbf{x}_s$ of the medial curve and also uncertainty in the radius $r_s$ of the discredited ribbon. 
But that there is range of distances $t \in 0\dots k_n$ from the medial curve which we can accept labeling as positive examples that are within the ribbon, and that there is some range of distances $t \in k_f\dots k_W$ which we can accept labeling as negative sample. 
Finally a range $t\in (k_n+1)...(k_f-1)$ of distances that are possible locations of the ribbon's boundary.
Therefore, when searching for improved medial curves and radii of the ribbon, we can consider a discrete range of offsets $t=-k_W,..., k_W$ chosen to be wide enough that true ribbon image itself likely fits entirely within the grid of input negative samples along its edges.

The orthorectified color image $\image(x,y)$
records the color at the point $x,y$ in the image plane.
Then $\image(\mathbf{x}_{s,t}),$ is a warped version of the image in which the ribbon is centered on a single strip at $t=0$.
The situation is illustrated in figure  \ref{fig:ribbon_3d}.  
In this warped image, we can estimate the amount $t_s$ to shift the ribbon's center in the $t-$axis, which is orthogonal to the curve,  and also the amount the radius $r_s$ so that the  ribbon at each row is in columns $(t_s - r_s)\dots(t_s+r_s)$.  
Our problem is to estimate the most likely values of $t_s$ and $r_s$.

@@

We use this assumption to estimate the probability that a pixel is part of a ribbon conditioned on its color.
Let $k_n$ be a parameter that describes the radius around the medial curve that we will consider to be part of the ribbon with very high confidence. 
Let $k_f$ indicate a distance from the medial curve that we consider very unlikely to be part of the ribbon. 
Finally, let $k_W$ indicate maximum value of $t$ to consider when learning the distribution of colors in a ribbon image. 
We model the distribution of colors within the sidewalk as a Gaussian Mixture Model of $k_g=4$ full-co-variance gaussian distribution and we model the distribution of colors outside of the ribbon as a mixture $2k_g$ Gaussian since we expect more variation and complexity in this zone. 
As shown in figure \ref{fig:GMM_result}, given an initial estimate for the set of colors inside or outside of the ribbon, we estimate the weights and co-variances of the Gaussians using the \ac{EM-GMM} \cite{sridharan2014gaussian} algorithm.

### 2018-08-20 Chapters/3.Hypothesis/Paper.tex
editing new figure and remove bad image
Updates from ShareLaTeX

\chapter{Experiment}

The main steps of our approach are illustrated in \figref{fig:Apparatus}; a \ac{VHR} orthorectified image is provided and a the approximate trajectory of a sidewalk is acquired from a \ac{GIS} such as \ac{OSM}.
Alternately, an approximate trajectory could be marked by a person to digitize the sidewalk quickly. 
The initial trajectory is re-sampled and used to warp a portion of aerial image so that the trajectory is mapped to a straight, horizontal line which we call a \textit{ribbon image}. 
We use a modest assumption that colors near the center of the ribbon image are more likely to be on a walking path in order to build a probability-density estimate for walking path materials. 
Based on the probability estimate at each pixel, we construct a single ribbon with priors that control the rate of change of thickness and direction of the ribbon. 
Finally, the boundaries are warped back onto the original reference frame. 
In this section we elaborate the process of generating a ribbon image, estimating the probability that a color belongs to the same material as a walking path, and the construction of a smooth ribbon image based on the resulting probabilities.

@@

@@

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\columnwidth]{Figures/GMM_sample6.png}
    \caption[\ac{GMM} Result 2]{Example of GMMs on sample sidewalk. Row 1 and 2 shows the foreground GMM for sample sidewalk, and row 3 and 4 shows the back-ground for simple sidewalk. We use grey-scale to show the changes of probabilities, where for foreground, white is more likely to be sidewalk, and black is not.}
    \label{fig:GMM_result_2}
\end{figure}

@@

@@

@@

>>>>

\chapter{Detail Experiments on \ac{DPST}}

The main steps of our approach are illustrated in \figref{fig:Apparatus}; a \ac{VHR} orthorectified image is provided by our sponsor and the approximate trajectory of a sidewalk is acquired from a \ac{GIS} such as \ac{OSM}.
Alternately, an approximate trajectory could be marked by a person to digitize the sidewalk quickly. 
The initial trajectory is re-sampled and used to warp a portion of aerial image so that the trajectory is mapped to a straight, horizontal line which we call a \textit{ribbon image}. 
We use a modest assumption that colors near the center of the ribbon image are more likely to be on a walking path in order to build a probability-density estimate for walking path materials. 
Based on the probability estimate at each pixel, we construct a single ribbon with priors that control the rate of change of thickness and direction of the ribbon. 
Finally, the boundaries are warped back onto the original reference frame. 
In this section we elaborate the process of generating a ribbon image, estimating the probability that a color belongs to the same material as a walking path, and the construction of a smooth ribbon image based on the resulting probabilities.

@@

\section{Validate Initial Trajectory}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/arizon_center.png}
    \caption[Demonstration on Arizona Center]{Detail demonstration on part of Arizona center, all sidewalks' \ac{GIS} information shows in Orange.}
    \label{fig:arizon_center}
\end{figure}

Before applying deep learning network to determine sidewalk's location, it's necessary to hand marking all sidewalk from imagery or extract the geometric information of each sidewalk from resources like \ac{OSM}. 
It's challenging since the geometric accuracy was not precise, which could cause performance issue since we rely on this information to segment the sidewalk part from maps for the next step. 
To ensure data accuracy, as shows in figure \ref{fig:arizon_center}, we spent days marking all sidewalks and their precise boundaries in Arizona Central for initial experiments. 
We can locate each sidewalk by using the geometric information and saved them into separate files. 
We also calculate the average sidewalk width from boundaries to decide reasonable window size in the following step.

@@

We develop a way to convert the given sidewalk into a ribbon image. 
As shown in figure \ref{fig:StraightenProcess}, we use the previous outcome (A) from the last step as input and connected all coordinate points data as the mid-line for the sample sidewalk. 
Then we apply a smooth function that we created to smooth the mid-line, so the shape of mid-line fits better to the actual sidewalk shape(B). 
We generate two parallel line as offsets on each side of the mid-line with a distance of twice the average width in between. 
Ideally even the mid-line is not perfectly laying on the middle, we would still fit the whole sidewalk into the ribbon image. 
For each point on the mid-line, we connect the corresponding points on both offsets to get the movement of the sidewalk and recorded them(C, D), we generate the straightened ribbon image by using the color data from each pixel in the points set that we record earlier(E). 
The image data in between each offset, with constant image width could be retrieved after that (F).
Then we reshape the image data to generate the ribbon image(G). 
Figure \ref{fig:Sample_Sidewalk_2} shows the complete ribbon-image output result on sample sidewalk. We separate it into parts to show better detail.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/straghten.pdf}
    \caption[Ribbon Image Generation]{Ribbon image generating process: from sub-figures A to G, we showed the step by step process to generate ribbon-image from a partial sidewalk. From raw input (A), we smoothed mid line and generated parallel off-site (B). Generated pixels (C) and connected each pixel to its correspond color data from the raw input (D). After gathered pixel data (E), we removed mid-line (F) and generated the ribbon image(G).}
    \label{fig:StraightenProcess}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{Figures/sample2_demo.png}
    \caption[Sample Sidewalk 2]{A ribbon image straighten output on sample sidewalk, row 1 shows the original input, row 2 to 5 show the ribbon image output separate into parts.}
    \label{fig:Sample_Sidewalk_2}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\columnwidth]{Figures/GMM_sample6.png}
    \caption[\ac{GMM} Result 2]{Example of GMMs on sample sidewalk. Row 1 and 2 shows the foreground GMM for sample sidewalk, and row 3 and 4 shows the back-ground for simple sidewalk. We use grey-scale to show the changes of probabilities, where for foreground, white is more likely to be sidewalk, and black is not.}
    \label{fig:GMM_result_2}
\end{figure}

@@

As shows in figure \ref{fig:GMM_Sample_2}, we applied a density estimation function to find the probability for each pixel in the ribbon image. 
For foreground density, we used grey-scale to determine the probability likely-hood for the sidewalk-feature, where white is more likely to be sidewalk and black is less likely. 
The background density is the opposite, which made black is more likely to be sidewalk and white is not. 
We use the log likely-hood function to calculate the foreground and background density and estimate density on pixels.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/GMM_SAMPLE2.png}
    \caption[Density Estimation on Sample Sidewalk]{A sample figure with density estimation applied on figure \ref{fig:Sample_Sidewalk_2}. Where white indicates pixels are more likely to be a sidewalk feature and black indicates pixels are more likely to be a non-sidewalk feature. We separate it into 4 parts from column 1 to 4.}
    \label{fig:GMM_Sample_2}
\end{figure}

@@

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=\textwidth]{Figures/3dcombine_top.png}
%     \caption[3D Ribbon Image]{An illustration of the parameters for a ribbon: the $k$ axis captures the thickness of the ribbon and the $i$ axis captures the distance along the initial ribbon, the $j$ axis records horizontal displacements from the initial ribbon's medial curve.}
%     \label{fig:3d_ribbon_top}
% \end{figure}

@@

We use our dynamic programming algorithm on the ribbon image to find the max score for each pixel that had better probability to be sidewalk feature that we mentioned in Chapter 4. 
More importantly, we introduce a penalty control function that makes each horizontal movement in the edges or center cost more than vertical movement. Basically, for each line of pixels, if they think the edges or center should shift more horizontally than one pixel compares to the last line, we score them with more penalty.

Figure \ref{fig:penalty} shows our algorithm managed to separate the driveway and sidewalk under the same feature as penalty increase. So we could apply the dynamic programming solution to locate the precise boundaries of given ribbon image. The penalty control improved our performance significantly. Because of this, our approach could predict the sidewalk under the tree shadow and other shadows or obstacles, which bring us more accurate result compare to other methods.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/penalty.png}
    \caption[Penalty Process]{Comparison with penalty change, we tested a variety of variables to decide which variable had best performance for width control. With the penalty increased at a reasonable amount, our algorithm decided not to recognize a driveway as sidewalk walk, in order to keep the sidewalk width consistent, even though they are the same texture.}
    \label{fig:penalty}
\end{figure}

As shown in figure \ref{fig:sample_result2}, after we generate the result on ribbon image, just need to simply covert the ribbon image back to its original shape by reverse the method that generates the ribbon image.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{Figures/sample2_result.png}
    \caption[Desire Output on Sample Sidewalk]{Detail demonstration on desire result after applying our dynamic programming approach. Where row 1 shows the result after reshape, row 2 to 5 shows the boundaries we calculated on ribbon image from \ref{fig:Sample_Sidewalk_2}.}
    \label{fig:sample_result2}
\end{figure}
